Probability

### 2016-04-18 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" add comments...

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
A possible space of events is the set
$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
projection $\mathbb{0}$ and the unit projection
$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
possible post-measurement state of a quantum system as follows: given some
arbitrary current quantum $\ket{\psi}$ to be measured, the event
$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
the event $\proj{1}$ states that the post-measurement state will be
$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
event $\mathbb{0}$ states that the post-measurement state will be the
empty state. Clearly irrespective of the current state $\ket{\psi}$
and irrespective of the particular experiment, the probability of
event $\mathbb{0}$ will always be 0 (it is an impossible event) and
the probability of event $\mathbb{1}$ will always be 1 (it is a
certain event). The probabilities attached to other events will depend
on the particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1 and the probability of event
$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
Hilbert space setup admits other possible spaces of events. For
example, another space of events could be
$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
$\proj{\ms}$ to the probability $\frac{1}{2}$.

>>>>

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
A possible space of events is the set
$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
projection $\mathbb{0}$ and the unit projection
$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
possible post-measurement state of a quantum system as follows: given some
arbitrary current quantum $\ket{\psi}$ to be measured, the event
$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
the event $\proj{1}$ states that the post-measurement state will be
$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
event $\mathbb{0}$ states that the post-measurement state will be the
empty state. \\
\yutsung{How about replacing the above sentence by something like: 
\begin{quote}
Each event is interpreted as a possible post-measurement state of
a quantum system if that event occurs as follows~\cite{Abramsky2013}:
...... and the event $\mathbb{0}$ does not to state the post-measurement
state because it never occurs. 
\end{quote}
}\\
Clearly irrespective of the current state $\ket{\psi}$
and irrespective of the particular experiment, the probability of
event $\mathbb{0}$ will always be 0 (it is an impossible event) and
the probability of event $\mathbb{1}$ will always be 1 (it is a
certain event). The probabilities attached to other events will depend
on the particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1 and the probability of event
$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
Hilbert space setup admits other possible spaces of events. For
example, another space of events could be
$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
$\proj{\ms}$ to the probability $\frac{1}{2}$.
